### 2022-01-11 paper/paper.tex
improve FMA contraction part using suggestions of Simon Byrne

As demonstrated in Section~\ref{sec:performance-comparison},
Julia is not generically slower than traditional high-performance programming
languages like C, C++, and Fortran. A minor exception is due to
Julia being built on top of LLVM, which does not perform the same optimizations as other
C/C++/Fortran compilers. In particular, LLVM does
not use fused multiply-add (FMA) instructions by default, while GCC and Intel
compilers do. Thus, one must opt-in to these optimizations explicitly.
Relying on Julia's code manipulation techniques, this can be achieved with the macro
\lstinline{@muladd}\footnote{\url{https://github.com/SciML/MuladdMacro.jl}}.

>>>>

As demonstrated in Section~\ref{sec:performance-comparison},
Julia is not generically slower than traditional high-performance programming
languages like C, C++, and Fortran. A minor exception in the context of scientific
computing relying on floating point operations is that Julia does not perform
automatic fused multiply-add (FMA) contraction, that is replacing a multiplication
followed by an addition with a single FMA instruction, as it is inconsistent
with its strict floating point semantics. In other compilers, this optimization
is controlled by a global compiler option (\lstinline{-ffp-contract} in GCC and
Clang) and often enabled at reasonable optimization levels such as \lstinline{-O2}
for GCC and Intel compilers\footnote{An interesting coincidence is that not only
Julia but most LLVM-based frontends tend not to enable FMA contraction by default.}.
In Julia, FMA contraction is controlled more locally: the
\lstinline{muladd}\footnote{\url{https://docs.julialang.org/en/v1/base/math/\#Base.muladd}}
intrinsic function allows the compiler to evaluate a multiply-add using the most
efficient method. Relying on Julia's code manipulation techniques, the
\lstinline{@muladd}\footnote{\url{https://github.com/SciML/MuladdMacro.jl}}
macro makes it convenient to use the \lstinline{muladd} function by
syntactically rewriting expressions to insert \lstinline{muladd} in appropriate
locations.
